---
title: "Create final sample (netmat, med, CNB)"
author: "Cedric Huchuan Xia"
date: "09/02/2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, message = FALSE, warning = FALSE,
	results = FALSE, eval = TRUE, cache = TRUE,
	 fig.width = 7, fig.height = 7, tidy = TRUE
)
knitr::opts_knit$set(root.dir = '/data/joy/BBL/projects/xiaNetworkCca/sCCA/aim1/')
```


```{r load packages, message=FALSE, warning=FALSE, cache=TRUE}
setwd('/data/joy/BBL/projects/xiaNetworkCca/sCCA/aim1/')
source('./script/chxRinitFunc.R')
```

```{r compile a master training sample}
healthx <- read.csv('/data/joy/BBL/studies/pnc/n1601_dataFreezeDec2016/health/n1601_health_20161214.csv')
mox <- read.csv('./result/201701/go1_motion.csv')
powx <- read.csv('./result/201701/go1_power.csv')
trainidx <- read.csv('./result/201701/go1train_subject.csv')
trainmaster <- merge(trainidx,mox)
trainmaster <- merge(trainmaster,powx)
trainmaster <- merge(trainmaster, healthx)
write.csv(trainmaster,'./result/201701/trainmaster.csv',quote=F,row.names=F)

#apply exclusion criteria. See below for the tally
trainsampleidx <- which(trainmaster$relMeanRMSmotion>0.2 |is.na(trainmaster$relMeanRMSmotion)==T | trainmaster$nframesHighMotionrms0.25>20 | trainmaster$powernummiss>1 | trainmaster$healthExcludev2 == 1)
trainsample <- trainmaster[-trainsampleidx,]
write.csv(trainsample,'./result/201701/trainsample.csv',quote=F,row.names=F)

testidx <- read.csv('./result/201701/go1test_subject.csv')
testmaster <- merge(testidx,mox)
testmaster <- merge(testmaster,powx)
testmaster <- merge(testmaster, healthx)
write.csv(testmaster,'./result/201701/testmaster.csv',quote=F,row.names=F)

#apply exclusion criteria. See below for the tally
testsampleidx <- which(testmaster$relMeanRMSmotion>0.2 |is.na(testmaster$relMeanRMSmotion)==T | testmaster$nframesHighMotionrms0.25>20 | testmaster$powernummiss>1 | testmaster$healthExcludev2 == 1 )
testsample <- testmaster[-testsampleidx,]
write.csv(testsample,'./result/201701/testsample.csv',quote=F,row.names=F)

```

## Training sample tally
#### For Power Analysis with psychopathology alone
#### Out of `r dim(trainidx)[1]` training subjects in Go1, `r length(trainsampleidx)` were excluded for the following criteria, leaving `r dim(trainsample)[1]` subjects:

##### 1. no usable rsfc scans (n=`r length(which(is.na(trainmaster$relMeanRMSmotion)==T))`)
##### 2. healthEx ==1 (n=`r length(which(trainmaster$healthExclude == 1))`)
##### 3. motion >0.2mm (n=`r length(which(trainmaster$relMeanRMSmotion>0.2))`)
##### 4. nframe >20 (n=`r length(which(trainmaster$nframesHighMotionrms0.25>20))`)
##### 5. uncovered power node >1 (n=`r length(which(trainmaster$powernummiss>1))`)

### Concatenate power,lausanne
```{r load appropriate rsfc network}
trainpower<-array(NA, c(264, 264, dim(trainsample)[1]))
for (i in 1:dim(trainsample)[1]){
  id <- trainsample$bblid[i]
  tp <- trainsample$datexscanid[i]
  powerpath<- paste("/data/joy/BBL/studies/pnc/processedData/restbold/restbold_201607151621/",id,"/",tp,"/net/264PowerPNC/",id,"_",tp,"_264PowerPNC_network.txt",sep="")
  trainpower[,,i] <- as.matrix(read.table(powerpath))
  print(paste(i,"."," copying ",id,"_",tp," network",sep=""))
  }

testpower<-array(NA, c(264, 264, dim(testsample)[1]))
for (i in 1:dim(testsample)[1]){
  id <- testsample$bblid[i]
  tp <- testsample$datexscanid[i]
  powerpath<- paste("/data/joy/BBL/studies/pnc/processedData/restbold/restbold_201607151621/",id,"/",tp,"/net/264PowerPNC/",id,"_",tp,"_264PowerPNC_network.txt",sep="")
  testpower[,,i] <- as.matrix(read.table(powerpath))
  print(paste(i,"."," copying ",id,"_",tp," network",sep=""))
  }
```

```{r save concatenated matrix}
save(trainpower, file ="./result/201701/go1_train_power_netmat.RData")
save(testpower, file ="./result/201701/go1_test_power_netmat.RData")
```

```{r make feature table of the matrix}
power.ft.train <-t(apply(trainpower,c(3),function(x) x[upper.tri(x, diag = F)]))
rownames(power.ft.train) <- trainsample$bblid
power.ft.train[is.na(power.ft.train)] <-0
write.csv(power.ft.train,"./result/201701/go1_train_power_ft.csv",quote=F)
save(power.ft.train,file ="./result/201701/go1_train_power_ft.RData")

power.ft.test <-t(apply(testpower,c(3),function(x) x[upper.tri(x, diag = F)]))
rownames(power.ft.test) <- testsample$bblid
power.ft.test[is.na(power.ft.test)] <-0
write.csv(power.ft.test,"./result/201701/go1_test_power_ft.csv",quote=F)
save(power.ft.test,file ="./result/201701/go1_test_power_ft.RData")
```

#### Power: `r dim(power.ft.train)[1]` subjects with `r dim(power.ft.train)[2]` unique edges
#### Laussane: `r dim(lau.ft.train)[1]` subjects with `r dim(lau.ft.train)[2]` unique edges

#### Average Network of Power for all training subjects
```{r average power net mat, echo=FALSE }
trainpowerave <- apply(trainpower, c(1,2), function(x) mean(na.omit(x)))
testpowerave <- apply(testpower, c(1,2), function(x) mean(na.omit(x)))

save(trainpowerave,testpowerave,file="./result/201701/net_power_ave.RData")
levelplot(testpowerave, at = seq(-1,1,length=10),par.settings = BuRdTheme(),xlab='',ylab='',main="Test Set")
levelplot(trainpowerave, at = seq(-1,1,length=10),par.settings = BuRdTheme(),xlab='',ylab='',main="Train Set")
```



### Compile clinical data for the training data 
``` {r clinical}
load('./result/201701/med_impute.RData')
trainsample <- read.csv('./result/201701/trainsample.csv')
med.train <- subset(med.final, is.element(med.final$bblid,trainsample$bblid)) 
testsample <- read.csv('./result/201701/testsample.csv')
med.test <- subset(med.final, is.element(med.final$bblid,testsample$bblid)) 
#save the 111 training sample
save(med.train,med.test,file= "./result/201701/med_cv_split.RData")
```
#### There are `r dim(meddata112.train)[1]` subjects with `r dim(meddata112.train)[2]-1` clinical items

