---
title: "Create Samples"
author: "Cedric Huchuan Xia"
date: "01/10/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE, message = FALSE, warning = FALSE,
	results = FALSE, eval = TRUE, cache = TRUE,
	 fig.width = 8, fig.height = 10, tidy = TRUE
)
knitr::opts_knit$set(root.dir = '~/Desktop/BBL/')
```

```{r load packages}
#source('./script/chxRinitFunc.R')
```

## Split 1601 into 2/3 and 1/3
```{r data split}
#load data release
setwd('~/Desktop/BBL/')
bifactor <- read.csv('./studies/pnc/n1601_dataFreeze/clinical/n1601_goassess_clinical_factor_scores_20161212.csv')
demogra <- read.csv('./studies/pnc/n1601_dataFreeze/demographics/n1601_demographics_go1_20161212.csv')
go1data <- merge(bifactor,demogra, by = "bblid")
go1tosplit <- go1data[,c('bblid','scanid.x','sex','race2','ageAtScan1','mood_4factor','psychosis_4factor','externalizing_4factor','phobias_4factor','overall_psychopathology_4factor')]
#remove any NA's
go1nona <- subset(go1tosplit,is.na(go1tosplit$overall_psychopathology_4factor)==FALSE)

#split the sample
set.seed(3456)
trainIndex <- createDataPartition(go1nona$overall_psychopathology_4factor, p = 0.667, list =F,times=1)
go1train <- go1nona[trainIndex,]
go1test <- go1nona[-trainIndex,]

#save the sample split
write.csv(go1train,'./result/201701/go1train_subject.csv',row.names=FALSE, quote=FALSE)
write.csv(go1test,'./result/201701/go1test_subject.csv',row.names=FALSE, quote=FALSE)
```
#### The final training set for go1 has `r dim(go1train)[1]` subjects.
#### The final testing set for go1 has `r dim(go1test)[1]` subjects.

## Visualize the sample split
```{r visualize the sample split, echo=FALSE}
train.title <- "Train"
y.label <- "Percentage"
numbin <- 15

train.sex <- ggplot(go1train,aes(sex)) +
  geom_bar(aes(y=..count../sum(..count..)*100),fill='pink',alpha=0.8, width =0.5) +
  theme(axis.ticks = element_blank()) +
	scale_x_discrete(limit = c("1", "2"), labels = c("male","female"))+
	xlab("Sex") + ylab(y.label) + ggtitle(train.title)

train.race <- ggplot(go1train,aes(race2)) +
	geom_bar(aes(y=..count../sum(..count..)*100),fill='red',alpha=0.8, width =0.5) +
	theme(axis.ticks = element_blank()) +
	scale_x_discrete(limit = c("1", "2","3"), labels = c("White","Black","Other"))+
	xlab("Sex") + ylab(y.label) + ggtitle(train.title)

binwidth.age <- diff(range(go1train$ageAtScan1/12))/numbin
train.age <- ggplot(go1train,aes(ageAtScan1/12)) +
	geom_histogram(aes(y=..count../sum(..count..)*100),binwidth=binwidth.age,fill='orange',alpha=0.8) +
	xlab("Age") + ylab(y.label) + ggtitle(train.title)

binwidth.mod <- diff(range(go1train$mood_4factor))/numbin
train.mood <- ggplot(go1train,aes(mood_4factor)) +
	geom_histogram(aes(y=..count../sum(..count..)*100),binwidth=binwidth.mod,fill='yellow',alpha=0.8) +
	xlab("Mood") + ylab(y.label) + ggtitle(train.title)

binwidth.psych <- diff(range(go1train$psychosis_4factor))/numbin
train.psych <- ggplot(go1train,aes(psychosis_4factor)) +
	geom_histogram(aes(y=..count../sum(..count..)*100),binwidth=binwidth.psych,fill='green',alpha=0.8) +
	xlab("Psychosis") + ylab(y.label) + ggtitle(train.title)

binwidth.ext <- diff(range(go1train$externalizing_4factor))/numbin
train.ext <- ggplot(go1train,aes(externalizing_4factor)) +
	geom_histogram(aes(y=..count../sum(..count..)*100),binwidth=binwidth.ext,fill='cyan',alpha=0.8) +
	xlab("Ext") + ylab(y.label) + ggtitle(train.title)

binwidth.pnb <- diff(range(go1train$phobias_4factor))/numbin
train.pnb <- ggplot(go1train,aes(phobias_4factor)) +
	geom_histogram(aes(y=..count../sum(..count..)*100),binwidth=binwidth.pnb,fill='blue',alpha=0.8) +
	xlab("Phb") + ylab(y.label) + ggtitle(train.title)

binwidth.allpsych <- diff(range(go1train$overall_psychopathology_4factor))/numbin
train.allpsych <- ggplot(go1train,aes(overall_psychopathology_4factor)) +
	geom_histogram(aes(y=..count../sum(..count..)*100),binwidth=binwidth.allpsych,fill='purple',alpha=0.8) +
	xlab("Overall Psych") + ylab(y.label) + ggtitle(train.title)

test.title <- "Test"

test.sex <- ggplot(go1test,aes(sex)) +
	geom_bar(aes(y=..count../sum(..count..)*100),fill='pink',alpha=0.5, width =0.5) +
	theme(axis.ticks = element_blank()) +
	scale_x_discrete(limit = c("1", "2"), labels = c("male","female"))+
	xlab("Sex") + ylab(y.label) + ggtitle(test.title)

test.race <- ggplot(go1test,aes(race2)) +
	geom_bar(aes(y=..count../sum(..count..)*100),fill='red',alpha=0.5, width =0.5) +
	theme(axis.ticks = element_blank()) +
	scale_x_discrete(limit = c("1", "2","3"), labels = c("White","Black","Other"))+
	xlab("Sex") + ylab(y.label) + ggtitle(test.title)

binwidth.age <- diff(range(go1test$ageAtScan1/12))/numbin
test.age <- ggplot(go1test,aes(ageAtScan1/12)) +
	geom_histogram(aes(y=..count../sum(..count..)*100),binwidth=binwidth.age,fill='orange',alpha=0.5) +
	xlab("Age") + ylab(y.label) + ggtitle(test.title)

binwidth.mod <- diff(range(go1test$mood_4factor))/numbin
test.mood <- ggplot(go1test,aes(mood_4factor)) +
	geom_histogram(aes(y=..count../sum(..count..)*100),binwidth=binwidth.mod,fill='yellow',alpha=0.5) +
	xlab("Mood") + ylab(y.label) + ggtitle(test.title)

binwidth.psych <- diff(range(go1test$psychosis_4factor))/numbin
test.psych <- ggplot(go1test,aes(psychosis_4factor)) +
	geom_histogram(aes(y=..count../sum(..count..)*100),binwidth=binwidth.psych,fill='green',alpha=0.5) +
	xlab("Psychosis") + ylab(y.label) + ggtitle(test.title)

binwidth.ext <- diff(range(go1test$externalizing_4factor))/numbin
test.ext <- ggplot(go1test,aes(externalizing_4factor)) +
	geom_histogram(aes(y=..count../sum(..count..)*100),binwidth=binwidth.ext,fill='cyan',alpha=0.5) +
	xlab("Ext") + ylab(y.label) + ggtitle(test.title)

binwidth.pnb <- diff(range(go1test$phobias_4factor))/numbin
test.pnb <- ggplot(go1test,aes(phobias_4factor)) +
	geom_histogram(aes(y=..count../sum(..count..)*100),binwidth=binwidth.pnb,fill='blue',alpha=0.5) +
	xlab("Phb") + ylab(y.label) + ggtitle(test.title)

binwidth.allpsych <- diff(range(go1test$overall_psychopathology_4factor))/numbin
test.allpsych <- ggplot(go1test,aes(overall_psychopathology_4factor)) +
	geom_histogram(aes(y=..count../sum(..count..)*100),binwidth=binwidth.allpsych,fill='purple',alpha=0.5) +
	xlab("Overall Psych") + ylab(y.label) + ggtitle(test.title)

data.split.plot<- plot_grid(train.sex, test.sex, train.race, test.race, train.age, test.age,
		  train.mood, test.mood, train.ext, test.ext, train.psych, test.psych,
		  train.pnb, test.pnb, train.allpsych, test.allpsych,
		   align = "h", nrow =4)

data.split.plot
```

## upload to plot.ly
```{r plot.ly}
library(plotly)

```

## Apply exclusion criteria
```{r build rsfc motion flags}
#load 1601 bblid
go1id <- read.csv('./data/n1601_bblid_scanid_dateid.csv')
go1id$datexscanid <- paste(go1id$dateid, 'x', go1id$scanid, sep='')

#load motion measures
go1.motion <- read.csv('./data/rsfc_quality.csv',row.names=NULL)
colnames(go1.motion)[1:2] <- c("bblid","datexscanid") 
temp<-merge(go1.motion[,c("bblid","datexscanid","relMeanRMSmotion","nframesHighMotionrms0.25")],go1id[,c("bblid","datexscanid")])

namotion <- subset(go1id[,c("bblid","datexscanid")],!is.element(go1id$bblid,go1.motion$bblid))
namotion$relMeanRMSmotion <- rep(NA,dim(namotion)[1])
namotion$nframesHighMotionrms0.25 <- rep(NA,dim(namotion)[1])
go1.all.motion <- rbind(temp,namotion)

write.csv(go1.all.motion,"./result/201701/go1_motion.csv",quote=F,row.names=F)
```
### Rsfc Motion exclusion
* `r length(which(go1.all.motion$relMeanRMSmotion>0.2 | go1.all.motion$nframesHighMotionrms0.25 >20))` subjects from `r dim(go1.motion)[1]` who had useable restbold failed the motion exclusion criteria
* The criteria are 1) relMeanRMSmotion > 0.2 mm (n=`r length(which(go1.all.motion$relMeanRMSmotion>0.2))`); or 2) nframesHighMotionrms0.25 > 20 (n=`r length(which(go1.all.motion$nframesHighMotionrms0.25 >20))`)

```{r network coverage: Power}
#load power network coverage
go1.powerqa <- read.csv('./data/go1powermissing.csv',header=F)
nodes <- as.character(go1.powerqa$V3)
go1.powerqa$powernummiss <- lengths(strsplit(as.character(nodes),' ', fixed= TRUE))
#go1.powerqa$V3 <- strsplit(as.character(nodes),' ', fixed= TRUE)
colnames(go1.powerqa)[1:3] <- c("bblid","datexscanid","powermissnodes")

napower <- subset(go1id[,c("bblid","datexscanid")],!is.element(go1id$bblid,go1.powerqa$bblid))
napower$powermissnodes <- rep(NA,dim(napower)[1])
napower$powernummiss <- rep(0,dim(napower)[1])
go1.all.power <- rbind(go1.powerqa,napower)

write.csv(go1.all.power,"./result/201701/go1_power.csv",quote=F,row.names=F)
```
### Rsfc network(power) exclusion
* `r length(which(go1.all.power$powernummiss >1))` subjects from `r dim(go1.motion)[1]` who had useable restbold failed the power network exclusion criteria
* The criteria is missing more than 1 node

```{r network coverage: Laussane}
#load Laussane network coverage
go1.lauqa <- read.csv('./data/go1laumissing.csv',header=F)
launodes <- as.character(go1.lauqa$V3)
go1.lauqa$launummiss <- lengths(strsplit(as.character(launodes),' ', fixed= TRUE))
#go1.lauqa$V3 <- strsplit(as.character(launodes),' ', fixed= TRUE)
colnames(go1.lauqa)[1:3] <- c("bblid","datexscanid","laumissnodes")

nalau <- subset(go1id[,c("bblid","datexscanid")],!is.element(go1id$bblid,go1.lauqa$bblid))
nalau$laumissnodes <- rep(NA,dim(nalau)[1])
nalau$launummiss <- rep(0,dim(nalau)[1])
go1.all.lau <- rbind(go1.lauqa,nalau)

write.csv(go1.all.lau,"./data/go1_lau.csv",quote=F,row.names=F)

```
### Rsfc network(Laussane) exclusion
* `r length(which(go1.all.lau$launummiss >1))` subjects from `r dim(go1.motion)[1]` who had useable restbold failed the Laussane network exclusion criteria
* The criteria is missing more than 1 node




